Informing forest carbon inventories under the Paris Agreement using the Global Forest Carbon Database (ForC v4.0)

### 2024-08-02 doc/manuscript/ForC-EFDB manuscript.Rmd
describe reasons for data rejection; remove litter, delta.litter
#64

n_ind_records_EFDB_variables= C_variables[length(C_variables[,"variable"]), "n independent records in ForC"] #n independent records relevant to EFDB
n_ind_records_agb <- C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_ag"]
n_ind_records_agb_components <- C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_ag_woody"] + C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_ag_foliage"]
n_ind_records_biomass <- C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass"]
n_ind_records_rootbiomass <- C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_root"] +C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_root_fine"]+C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_root_coarse"]
n_ind_records_deadwood <- C_variables$`n independent records in ForC`[C_variables$`variable` == "deadwood"] +C_variables$`n independent records in ForC`[C_variables$`variable` == "deadwood_down"]+C_variables$`n independent records in ForC`[C_variables$`variable` == "deadwood_standing"]
n_ind_records_OL <- C_variables$`n independent records in ForC`[C_variables$`variable` == "litter"] +C_variables$`n independent records in ForC`[C_variables$`variable` == "O.horizon"]
n_ind_records_TotEcosystemC <- C_variables$`n independent records in ForC`[C_variables$`variable` == "total.ecosystem_2"] 
n_ind_records_SOC <- C_variables$`n independent records in ForC`[C_variables$`variable` == "SOM / SOC"] 
n_ind_records_deltaagb <- C_variables$`n independent records in ForC`[C_variables$`variable` == "delta.agb"] 
n_ind_records_deltaOL <- C_variables$`n independent records in ForC`[C_variables$`variable` == "delta.O.horizon"] 
flux_variables_with_records <- c("NPP_woody", "ANPP_woody", "ANPP_woody_stem", "ANPP_woody_branch", "woody.mortality_ag", "BNPP_root", "BNPP_root_fine","BNPP_root.turnover_fine","BNPP_root_coarse" , "ANPP_litterfall", "NPP_litter", "R_het_litter")
n_ind_records_flux <- sum(C_variables$`n independent records in ForC`[C_variables$`variable` %in% flux_variables_with_records])

n_records_reviewed_or_added= C_variables[length(C_variables[,"variable"]), "n reviewed"]
n_records_added = max(ForC_measurements$measurement.ID) -48956 # Madison's entries start with measurement.ID = 48956
n_records_checked = n_records_reviewed_or_added - n_records_added # this will be hard to get at, but we can at least estimate a minimum (= previously existing records in records sent to EFDB)

n_records_sent_to_EFDB = C_variables[length(C_variables[,"variable"]), "n submitted to EFDB"] # n records sent to EFDB
n_relevant_variables_no_records_sent =  sum(C_variables$`n submitted to EFDB` == 0,  na.rm = TRUE)
n_relevant_variables_records_sent= n_relevant_variables - n_relevant_variables_no_records_sent
n_records_sent_biomass<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass"]
n_records_sent_agb <- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_ag"]
n_records_sent_agb_components <- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_ag_woody"] + C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_ag_foliage"]
n_records_sent_rootbiomass <- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_root"] 
n_records_sent_rootbiomass_components <- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_root_fine"]+C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_root_coarse"]
n_records_sent_deadwood<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "deadwood"] 
n_records_sent_deadwood_components<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "deadwood_down"]+C_variables$`n submitted to EFDB`[C_variables$`variable` == "deadwood_standing"]
n_records_sent_litter<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "litter"] +C_variables$`n submitted to EFDB`[C_variables$`variable` == "O.horizon"]
n_records_sent_soil<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "SOM / SOC"] 
n_records_sent_stocks = n_records_sent_biomass+n_records_sent_agb+n_records_sent_agb_components+n_records_sent_rootbiomass+n_records_sent_rootbiomass_components+n_records_sent_deadwood+n_records_sent_deadwood_components+ n_records_sent_litter+ n_records_sent_soil
n_records_sent_delta.agb<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "delta.agb"]
n_records_sent_delta.litter<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "delta.O.horizon"]+C_variables$`n submitted to EFDB`[C_variables$`variable` == "delta.litter"]
n_records_sent_increments <- n_records_sent_delta.agb+n_records_sent_delta.litter
n_records_sent_fluxes <- sum(C_variables$`n submitted to EFDB`[C_variables$`variable` %in% flux_variables_with_records])
n_records_sent_fluxes_check = n_records_sent_to_EFDB-n_records_sent_stocks-n_records_sent_increments

@@

![**Figure `r fig_variable_mapping`. Schematic illustrating the carbon pools defined under IPCC Guidelines for national greenhouse gas inventories; corresponding ForC variables, and relationships among them.** For each C pool, we show ForC variables corresponding to the stock, net annual increment, influx, and outflux. Most, but not all, EFDB-relevant ForC variables are shown here. Correspondence of ForC variables to IPCC criteria often depends upon measurement protocols (e.g., minimum stem diameter censused). Additional caveats are as follows: (a,b) branch fall and mortality of stems below the minimum stem diameter censused, which are necessary for a full accounting of dead organic matter production but typically assumed negligible for calculations of biomass change, are excluded by common measurement practice (a) or ForC variable definition (b); (c) assumes that leaf production equals leaf fall, or that changes in foliage biomass are negligble; (d,e) belowground components excluded by common measurement practice (d) or ForC variable definition (e); (f) excludes movement of dead wood into litter through breakage or size reduction; (g) measurements often limited to litter horizon (OL) and may exclude larger branches and stems classified as litter and/or the more decomposed layers of the O horizon. **This variable is techically EFDB-relevant but not selected for submission because their is no corresponding influx variable.](figures_tables/C_variable_mapping.png)

@@

As of `r format(Sys.time(), '%B %d, %Y')`<!--inserts date upon knit-->, ForC (v4.0) contained `r n_independent_records_ForC` independent records (`r n_records_ForC` total), `r n_ind_records_EFDB_variables` of which were for the `r n_relevant_variables` variables relevant to EFDB (Fig. `r fig_variable_mapping`).
We had reviewed or added `r n_records_reviewed_or_added` records for submission to EFDB, `r n_records_sent_to_EFDB` of which met the criteria for submission, and `r n_records_posted_EFDB` of which had been reviewed by EFDB's review panel, accepted, and posted (`r table_variables`).
The `r round((n_records_reviewed_or_added -n_records_sent_to_EFDB )/n_records_reviewed_or_added,2)*100`% discrepancy between records we reviewed and those submitted to EFDB was due to the presence of digitized records and records where a variable's value had been calculated as the sum or difference of related variables rather than presented directly in the text.
The discrepancy between the number of records sent and that posted to EFDB is because some records (`r round((1-(n_records_posted_EFDB/n_records_sent_to_EFDB)),2)*100`%) were deemed not applicable to EFDB by the review panel.
As of `r format(Sys.time(), '%B %d, %Y')`, the `r n_records_sent_to_EFDB` ForC records posted in EFDB represented `r percent_forest_records`% of the total EFDB records for forest land.

ForC v4.0 contained records for `r n_relevant_variables_with_data` of the `r n_relevant_variables` variables (or closely-related variable groups) relevant to EFDB (Fig. `r fig_variable_mapping`,  `r table_variables`).
Records were submitted for `r n_relevant_variables_records_sent` variables (or closely-related variable groups), including variables from each C pool (`r table_variables`).
The records available in ForC v4.0 -- and the subset submitted to EFDB -- were very unevenly distributed across variables (`r table_variables`). 
The majority (`r round(n_records_sent_stocks/n_records_sent_to_EFDB, 2)*100`%) of records submitted were for C stocks, including
`r round(n_records_sent_biomass/n_records_sent_to_EFDB,2)*100`% for total biomass, 
`r round(n_records_sent_agb/n_records_sent_to_EFDB,2)*100`% for aboveground biomass,
`r round(n_records_sent_agb_components/n_records_sent_to_EFDB,2)*100`% for components of aboveground biomass (wood or foliage), 
`r round(n_records_sent_rootbiomass/n_records_sent_to_EFDB,2)*100`% for root biomass, 
`r round(n_records_sent_rootbiomass_components/n_records_sent_to_EFDB,2)*100`% for components of root biomass (coarse or fine roots), 
`r round(n_records_sent_deadwood/n_records_sent_to_EFDB,2)*100`% for dead wood, 
`r round(n_records_sent_deadwood_components/n_records_sent_to_EFDB,2)*100`% for components of dead wood (standing or fallen), 
`r round(n_records_sent_litter/n_records_sent_to_EFDB,2)*100`% for litter (entire O horizon or OL layer component),
and `r round(n_records_sent_soil/n_records_sent_to_EFDB,2)*100`% for SOM/ SOC.
Increment records totaled `r round(n_records_sent_increments/n_records_sent_to_EFDB*100, 0)`% of records submitted, all but four of which described aboveground biomass.
The remaining `r round(n_records_sent_fluxes/n_records_sent_to_EFDB*100, 0)`% of records submitted described fluxes, all of which were either inputs or outputs to the aboveground biomass pool, a subset of which also described inputs to the dead wood or litter pool (Fig. `r fig_variable_mapping`,`r table_variables`).

>>>>

n_ind_records_EFDB_variables= C_variables[length(C_variables[,"variable"]), "n independent records in ForC"] #n independent records relevant to EFDB
n_ind_records_agb <- C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_ag"]
n_ind_records_agb_components <- C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_ag_woody"] + C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_ag_foliage"]
n_ind_records_biomass <- C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass"]
n_ind_records_rootbiomass <- C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_root"] +C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_root_fine"]+C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_root_coarse"]
n_ind_records_deadwood <- C_variables$`n independent records in ForC`[C_variables$`variable` == "deadwood"] +C_variables$`n independent records in ForC`[C_variables$`variable` == "deadwood_down"]+C_variables$`n independent records in ForC`[C_variables$`variable` == "deadwood_standing"]
n_ind_records_OL <- C_variables$`n independent records in ForC`[C_variables$`variable` == "O.horizon"]
n_ind_records_TotEcosystemC <- C_variables$`n independent records in ForC`[C_variables$`variable` == "total.ecosystem_2"] 
n_ind_records_SOC <- C_variables$`n independent records in ForC`[C_variables$`variable` == "SOM / SOC"] 
n_ind_records_deltaagb <- C_variables$`n independent records in ForC`[C_variables$`variable` == "delta.agb"] 
n_ind_records_deltaOL <- C_variables$`n independent records in ForC`[C_variables$`variable` == "delta.O.horizon"] 
flux_variables_with_records <- c("NPP_woody", "ANPP_woody", "ANPP_woody_stem", "ANPP_woody_branch", "woody.mortality_ag", "BNPP_root", "BNPP_root_fine","BNPP_root.turnover_fine","BNPP_root_coarse" , "ANPP_litterfall", "NPP_litter", "R_het_litter")
n_ind_records_flux <- sum(C_variables$`n independent records in ForC`[C_variables$`variable` %in% flux_variables_with_records])

n_records_rejected_variables = 23+5  # 23 litter, 5 NEE

n_records_reviewed_or_added= C_variables[length(C_variables[,"variable"]), "n reviewed"] + n_records_rejected_variables
n_records_added = max(ForC_measurements$measurement.ID) -48956 # Madison's entries start with measurement.ID = 48956
n_records_checked = n_records_reviewed_or_added - n_records_added  # this is hard to get at, but we can at least estimate a minimum (= previously existing records in records sent to EFDB)

n_records_sent_to_EFDB =  C_variables[length(C_variables[,"variable"]), "n submitted to EFDB"] + n_records_rejected_variables  # n records sent to EFDB
n_relevant_variables_no_records_sent =  sum(C_variables$`n submitted to EFDB` == 0,  na.rm = TRUE)
n_relevant_variables_records_sent= n_relevant_variables - n_relevant_variables_no_records_sent
n_records_sent_biomass<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass"]
n_records_sent_agb <- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_ag"]
n_records_sent_agb_components <- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_ag_woody"] + C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_ag_foliage"]
n_records_sent_rootbiomass <- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_root"] 
n_records_sent_rootbiomass_components <- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_root_fine"]+C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_root_coarse"]
n_records_sent_deadwood<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "deadwood"] 
n_records_sent_deadwood_components<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "deadwood_down"]+C_variables$`n submitted to EFDB`[C_variables$`variable` == "deadwood_standing"]
n_records_sent_litter<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "O.horizon"]
n_records_sent_soil<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "SOM / SOC"] 
n_records_sent_stocks = n_records_sent_biomass+n_records_sent_agb+n_records_sent_agb_components+n_records_sent_rootbiomass+n_records_sent_rootbiomass_components+n_records_sent_deadwood+n_records_sent_deadwood_components+ n_records_sent_litter+ n_records_sent_soil
n_records_sent_delta.agb<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "delta.agb"]
n_records_sent_delta.litter<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "delta.O.horizon"]
n_records_sent_increments <- n_records_sent_delta.agb+n_records_sent_delta.litter
n_records_sent_fluxes <- sum(C_variables$`n submitted to EFDB`[C_variables$`variable` %in% flux_variables_with_records])
n_records_sent_fluxes_check = n_records_sent_to_EFDB-n_records_sent_stocks-n_records_sent_increments

@@

![**Figure `r fig_variable_mapping`. Schematic illustrating the carbon pools defined under IPCC Guidelines for national greenhouse gas inventories; corresponding ForC variables, and relationships among them.** For each C pool, we show ForC variables corresponding to the stock, net annual increment, influx, and outflux. Most, but not all, EFDB-relevant ForC variables are shown here. Correspondence of ForC variables to IPCC criteria often depends upon measurement protocols (e.g., minimum stem diameter censused). Additional caveats are as follows: (a,b) branch fall and mortality of stems below the minimum stem diameter censused, which are necessary for a full accounting of dead organic matter production but typically assumed negligible for calculations of biomass change, are excluded by common measurement practice (a) or ForC variable definition (b); (c) assumes that leaf production equals leaf fall, or that changes in foliage biomass are negligble; (d,e) belowground components excluded by common measurement practice (d) or ForC variable definition (e); (f) excludes movement of dead wood into litter through breakage or size reduction; (g) measurements often limited to litter layer (OL) and may exclude larger branches and stems classified as litter and/or the more decomposed layers of the O horizon. **This variable is techically EFDB-relevant but not selected for submission because their is no corresponding influx variable.](figures_tables/C_variable_mapping.png)

@@

As of `r format(Sys.time(), '%B %d, %Y')`<!--inserts date upon knit-->, ForC (v4.0) contained `r n_independent_records_ForC` independent records (`r n_records_ForC` total), `r n_ind_records_EFDB_variables` of which were for the `r n_relevant_variables` variables relevant to EFDB (Fig. `r fig_variable_mapping`).
We had reviewed or added `r n_records_reviewed_or_added` records for submission to EFDB, `r n_records_sent_to_EFDB` of which had been submitted, and `r n_records_posted_EFDB` of which had been reviewed by EFDB's review panel, accepted, and posted (`r table_variables`).
The `r round((n_records_reviewed_or_added -n_records_sent_to_EFDB )/n_records_reviewed_or_added,2)*100`% discrepancy between records we reviewed and those submitted to EFDB was due to the presence of digitized records and records where a variable's value had been calculated as the sum or difference of related variables rather than presented directly in the text.
The discrepancy between the number of records submitted and that posted to EFDB is because some records (`r round((1-(n_records_posted_EFDB/n_records_sent_to_EFDB)),2)*100`%) were deemed not applicable to EFDB by the review panel.
Reasons included -- but were not limited to -- non-applicability to the IPCC methodology of the variable submitted (e.g., net ecosystem CO~2~ exchange, litter - OL layer; subsequently excluded from lists of relevant variables and counts of relevant records), inadequate information on the quality of data and thus on its replicability (e.g., confidence interval/uncertainty), and vaguely described disturbance histories (e.g., "moderately"/ "severely" burned). 
As of `r format(Sys.time(), '%B %d, %Y')`, the `r n_records_sent_to_EFDB` ForC records posted in EFDB represented `r percent_forest_records`% of the total EFDB records for forest land.

ForC v4.0 contained records for `r n_relevant_variables_with_data` of the `r n_relevant_variables` variables (or closely-related variable groups) relevant to EFDB (Fig. `r fig_variable_mapping`,  `r table_variables`).
Records were submitted for `r n_relevant_variables_records_sent` variables (or closely-related variable groups), including variables from each C pool (`r table_variables`).
The records available in ForC v4.0 -- and the subset submitted to EFDB -- were very unevenly distributed across variables (`r table_variables`). 
The majority (`r round(n_records_sent_stocks/n_records_sent_to_EFDB, 2)*100`%) of records submitted were for C stocks, including
`r round(n_records_sent_biomass/n_records_sent_to_EFDB,2)*100`% for total biomass, 
`r round(n_records_sent_agb/n_records_sent_to_EFDB,2)*100`% for aboveground biomass,
`r round(n_records_sent_agb_components/n_records_sent_to_EFDB,2)*100`% for components of aboveground biomass (wood or foliage), 
`r round(n_records_sent_rootbiomass/n_records_sent_to_EFDB,2)*100`% for root biomass, 
`r round(n_records_sent_rootbiomass_components/n_records_sent_to_EFDB,2)*100`% for components of root biomass (coarse or fine roots), 
`r round(n_records_sent_deadwood/n_records_sent_to_EFDB,2)*100`% for dead wood, 
`r round(n_records_sent_deadwood_components/n_records_sent_to_EFDB,2)*100`% for components of dead wood (standing or fallen), 
`r round(n_records_sent_litter/n_records_sent_to_EFDB,2)*100`% for litter (entire O horizon),
and `r round(n_records_sent_soil/n_records_sent_to_EFDB,2)*100`% for SOM/ SOC.
Increment records totaled `r round(n_records_sent_increments/n_records_sent_to_EFDB*100, 0)`% of records submitted, all but four of which described aboveground biomass.
The remaining `r round(n_records_sent_fluxes/n_records_sent_to_EFDB*100, 0)`% of records submitted described fluxes, all of which were either inputs or outputs to the aboveground biomass pool, a subset of which also described inputs to the dead wood or litter pool (Fig. `r fig_variable_mapping`,`r table_variables`).

### 2024-08-02 doc/manuscript/SI_ForCv40.Rmd
describe reasons for data rejection; remove litter, delta.litter
#64

```{r eval = TRUE, echo=FALSE, warning=FALSE, results='hide'}
#Tables
table_pools =1
table_recommendations = 2

#Figures
fig_variable_mapping=1
fig_map=2
fig_histograms=3

@@

n_ind_records_EFDB_variables= C_variables[length(C_variables[,"variable"]), "n independent records in ForC"] #n independent records relevant to EFDB
n_ind_records_agb <- C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_ag"]
n_ind_records_agb_components <- C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_ag_woody"] + C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_ag_foliage"]
n_ind_records_biomass <- C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass"]
n_ind_records_rootbiomass <- C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_root"] +C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_root_fine"]+C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_root_coarse"]
n_ind_records_deadwood <- C_variables$`n independent records in ForC`[C_variables$`variable` == "deadwood"] +C_variables$`n independent records in ForC`[C_variables$`variable` == "deadwood_down"]+C_variables$`n independent records in ForC`[C_variables$`variable` == "deadwood_standing"]
n_ind_records_OL <- C_variables$`n independent records in ForC`[C_variables$`variable` == "litter"] +C_variables$`n independent records in ForC`[C_variables$`variable` == "O.horizon"]
n_ind_records_TotEcosystemC <- C_variables$`n independent records in ForC`[C_variables$`variable` == "total.ecosystem_2"] 
n_ind_records_SOC <- C_variables$`n independent records in ForC`[C_variables$`variable` == "SOM / SOC"] 
n_ind_records_deltaagb <- C_variables$`n independent records in ForC`[C_variables$`variable` == "delta.agb"] 
n_ind_records_deltaOL <- C_variables$`n independent records in ForC`[C_variables$`variable` == "delta.O.horizon"] 
flux_variables_with_records <- c("NPP_woody", "ANPP_woody", "ANPP_woody_stem", "ANPP_woody_branch", "woody.mortality_ag", "BNPP_root", "BNPP_root_fine","BNPP_root.turnover_fine","BNPP_root_coarse" , "ANPP_litterfall", "NPP_litter", "R_het_litter")
n_ind_records_flux <- sum(C_variables$`n independent records in ForC`[C_variables$`variable` %in% flux_variables_with_records])

n_records_reviewed_or_added= C_variables[length(C_variables[,"variable"]), "n reviewed"]
n_records_added = max(ForC_measurements$measurement.ID) -48956 # Madison's entries start with measurement.ID = 48956
n_records_checked = n_records_reviewed_or_added - n_records_added # this will be hard to get at, but we can at least estimate a minimum (= previously existing records in records sent to EFDB)

n_records_sent_to_EFDB = C_variables[length(C_variables[,"variable"]), "n submitted to EFDB"] # n records sent to EFDB
n_relevant_variables_no_records_sent =  sum(C_variables$`n submitted to EFDB` == 0,  na.rm = TRUE)
n_relevant_variables_records_sent= n_relevant_variables - n_relevant_variables_no_records_sent
n_records_sent_biomass<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass"]
n_records_sent_agb <- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_ag"]
n_records_sent_agb_components <- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_ag_woody"] + C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_ag_foliage"]
n_records_sent_rootbiomass <- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_root"] 
n_records_sent_rootbiomass_components <- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_root_fine"]+C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_root_coarse"]
n_records_sent_deadwood<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "deadwood"] 
n_records_sent_deadwood_components<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "deadwood_down"]+C_variables$`n submitted to EFDB`[C_variables$`variable` == "deadwood_standing"]
n_records_sent_litter<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "litter"] +C_variables$`n submitted to EFDB`[C_variables$`variable` == "O.horizon"]
n_records_sent_soil<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "SOM / SOC"] 
n_records_sent_stocks = n_records_sent_biomass+n_records_sent_agb+n_records_sent_agb_components+n_records_sent_rootbiomass+n_records_sent_rootbiomass_components+n_records_sent_deadwood+n_records_sent_deadwood_components+ n_records_sent_litter+ n_records_sent_soil
n_records_sent_delta.agb<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "delta.agb"]
n_records_sent_delta.litter<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "delta.O.horizon"]+C_variables$`n submitted to EFDB`[C_variables$`variable` == "delta.litter"]
n_records_sent_increments <- n_records_sent_delta.agb+n_records_sent_delta.litter
n_records_sent_fluxes <- sum(C_variables$`n submitted to EFDB`[C_variables$`variable` %in% flux_variables_with_records])
n_records_sent_fluxes_check = n_records_sent_to_EFDB-n_records_sent_stocks-n_records_sent_increments

n_records_posted_EFDB = 376 # n records accepted and posted in EFDB (easy to determine by entering "ForC" in the "Other Properties" search field of EFDB: https://www.ipcc-nggip.iges.or.jp/EFDB/find_ef.php. Then get number from upper left box where it says "displayed records")

n_new_variables = 11 + 2 + 2 #delta. + woody.mortality + O horizon
# get n fields modified
sampling_details <- read.csv(paste0(path_to_ForC,"/ForC/database_management_records/record_of_changes.csv"), stringsAsFactors = FALSE, check.names = FALSE)
n_fields_modified =  length(sampling_details[,"Column"]) + 4

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE, results='hide'}
#Tables
#Tables
table_pools =1
table_recommendations = 2

#Figures
fig_variable_mapping=1
fig_map=2
fig_climate=3
fig_histograms=4

@@

n_ind_records_EFDB_variables= C_variables[length(C_variables[,"variable"]), "n independent records in ForC"] #n independent records relevant to EFDB
n_ind_records_agb <- C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_ag"]
n_ind_records_agb_components <- C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_ag_woody"] + C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_ag_foliage"]
n_ind_records_biomass <- C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass"]
n_ind_records_rootbiomass <- C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_root"] +C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_root_fine"]+C_variables$`n independent records in ForC`[C_variables$`variable` == "biomass_root_coarse"]
n_ind_records_deadwood <- C_variables$`n independent records in ForC`[C_variables$`variable` == "deadwood"] +C_variables$`n independent records in ForC`[C_variables$`variable` == "deadwood_down"]+C_variables$`n independent records in ForC`[C_variables$`variable` == "deadwood_standing"]
n_ind_records_OL <- C_variables$`n independent records in ForC`[C_variables$`variable` == "O.horizon"]
n_ind_records_TotEcosystemC <- C_variables$`n independent records in ForC`[C_variables$`variable` == "total.ecosystem_2"] 
n_ind_records_SOC <- C_variables$`n independent records in ForC`[C_variables$`variable` == "SOM / SOC"] 
n_ind_records_deltaagb <- C_variables$`n independent records in ForC`[C_variables$`variable` == "delta.agb"] 
n_ind_records_deltaOL <- C_variables$`n independent records in ForC`[C_variables$`variable` == "delta.O.horizon"] 
flux_variables_with_records <- c("NPP_woody", "ANPP_woody", "ANPP_woody_stem", "ANPP_woody_branch", "woody.mortality_ag", "BNPP_root", "BNPP_root_fine","BNPP_root.turnover_fine","BNPP_root_coarse" , "ANPP_litterfall", "NPP_litter", "R_het_litter")
n_ind_records_flux <- sum(C_variables$`n independent records in ForC`[C_variables$`variable` %in% flux_variables_with_records])

n_records_rejected_variables = 23+5  # 23 litter, 5 NEE

n_records_reviewed_or_added= C_variables[length(C_variables[,"variable"]), "n reviewed"] + n_records_rejected_variables
n_records_added = max(ForC_measurements$measurement.ID) -48956 # Madison's entries start with measurement.ID = 48956
n_records_checked = n_records_reviewed_or_added - n_records_added  # this is hard to get at, but we can at least estimate a minimum (= previously existing records in records sent to EFDB)

n_records_sent_to_EFDB =  C_variables[length(C_variables[,"variable"]), "n submitted to EFDB"] + n_records_rejected_variables  # n records sent to EFDB
n_relevant_variables_no_records_sent =  sum(C_variables$`n submitted to EFDB` == 0,  na.rm = TRUE)
n_relevant_variables_records_sent= n_relevant_variables - n_relevant_variables_no_records_sent
n_records_sent_biomass<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass"]
n_records_sent_agb <- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_ag"]
n_records_sent_agb_components <- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_ag_woody"] + C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_ag_foliage"]
n_records_sent_rootbiomass <- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_root"] 
n_records_sent_rootbiomass_components <- C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_root_fine"]+C_variables$`n submitted to EFDB`[C_variables$`variable` == "biomass_root_coarse"]
n_records_sent_deadwood<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "deadwood"] 
n_records_sent_deadwood_components<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "deadwood_down"]+C_variables$`n submitted to EFDB`[C_variables$`variable` == "deadwood_standing"]
n_records_sent_litter<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "O.horizon"]
n_records_sent_soil<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "SOM / SOC"] 
n_records_sent_stocks = n_records_sent_biomass+n_records_sent_agb+n_records_sent_agb_components+n_records_sent_rootbiomass+n_records_sent_rootbiomass_components+n_records_sent_deadwood+n_records_sent_deadwood_components+ n_records_sent_litter+ n_records_sent_soil
n_records_sent_delta.agb<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "delta.agb"]
n_records_sent_delta.litter<- C_variables$`n submitted to EFDB`[C_variables$`variable` == "delta.O.horizon"]
n_records_sent_increments <- n_records_sent_delta.agb+n_records_sent_delta.litter
n_records_sent_fluxes <- sum(C_variables$`n submitted to EFDB`[C_variables$`variable` %in% flux_variables_with_records])
n_records_sent_fluxes_check = n_records_sent_to_EFDB-n_records_sent_stocks-n_records_sent_increments

n_records_posted_EFDB = 1068 # n records accepted and posted in EFDB (easy to determine by entering "ForC" in the "Other Properties" search field of EFDB: https://www.ipcc-nggip.iges.or.jp/EFDB/find_ef.php. Then get number from upper left box where it says "displayed records". Updated Jan 2024)
percent_forest_records = round(n_records_posted_EFDB/5644*100,0); #as of Jan 2024

n_new_variables = 11 + 2 + 2 #delta. + woody.mortality + O horizon
# get n fields modified
sampling_details <- read.csv(paste0(path_to_ForC,"/ForC/database_management_records/record_of_changes.csv"), stringsAsFactors = FALSE, check.names = FALSE)
n_fields_modified =  length(sampling_details[,"Field"]) + 4
